Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-03-18 Cost_manuscript.Rmd
reverted section title format

### *Methods*
#### **Participants**

@@

#### **Foraging Task**

@@

#### **Operationalization of Cost**

@@

#### **Analyses**

@@

### *Results*
#### **Between-subjects: Decision Makers Integrate Delay and Reward Information**

@@

#### **Between-subjects: Consistency and Stability**

@@

#### **Foraging Task Adaptation**

@@

### *Results*
#### **Within-subjects: Decision Makers Integrate Reward Information**

@@

#### **Within-subjects: Consistency and Stability**

@@

### *Methods*
#### **Model Fitting and Model Comparison Procedures**

@@

#### **Model Definitions**

@@

### *Results*

@@

### Conclusion

>>>>

### **Methods**
#### *Participants*

@@

#### *Foraging Task*

@@

#### *Operationalization of Cost*

@@

#### *Analyses*

@@

### **Results**
#### *Between-subjects: Decision Makers Integrate Delay and Reward Information*

@@

#### *Between-subjects: Consistency and Stability*

@@

#### *Foraging Task Adaptation*

@@

### **Results**
#### *Within-subjects: Decision Makers Integrate Reward Information*

@@

#### *Within-subjects: Consistency and Stability*

@@

### **Methods**
#### *Model Fitting and Model Comparison Procedures*

@@

#### *Model Definitions*

@@

### **Results**

@@

### **Conclusion**
